---
title: "How to create a personograph"
author: "Grant COble-Neal"
format: revealjs
editor: visual
---

## Overview

A [personograph](https://github.com/joelkuiper/personograph) is a pictographic representation of relative harm and benefit from an intervention. The idea is to use icons to represent features of a given dataset.

## Notes

The folllowing notes are relevant:

-   A custom icon can be used. This requires importing an icon via the package [grImport](https://cran.r-project.org/web/packages/grImport/grImport.pdf).

-   The custom icon must be a postscript file. The format `.eps` works

## Code example 1

Personograph from the personograph documentation

```{r, echo = TRUE}
library(personograph)
data <- list(first=0.89, second=0.06, third=0.05)
# With colors
personograph(data, n.icons=64, dimensions=c(8, 8), colors=list(first="grey", second="blue", third="red"),
             fig.title = "Example of a personograph")

```

## Code example 2

Custom icon

```{r, echo=TRUE}
library(grImport)
library(personograph)
library(tidyverse)

mtcars.1 <- mtcars %>% 
  mutate(cylinders = as.factor(cyl)) %>% 
  group_by(cylinders) %>%
  summarise(cnt = n()) %>% 
  mutate(proportions = round(cnt) / sum(cnt), 1) %>% 
  arrange((desc(proportions))) %>% 
  column_to_rownames("cylinders") %>% 
  select(proportions)
  
rownames(mtcars.1) <- english::as.english(as.numeric(rownames(mtcars.1)))

mtcars.2 <- mtcars.1 %>% 
  rownames_to_column("cylinders") %>% 
  pivot_wider(values_from = proportions, names_from = cylinders)

grImport::PostScriptTrace(here::here("images", "SV01-Car-Side-On.eps"), outfilename = "car.ps")
car.1 <- grImport::readPicture("car.ps")
data <- as.list(mtcars.2)

personograph(data, n.icons=100, dimensions=c(10, 10), colors=list(eight = "grey", four = "blue", six = "red"),
             fig.title = "Cars by number of cylinders",
             fig.cap = "Source: R-datasets; mtcars",
             icon =  car.1)
```
